Algorithmically Trading like a Human with GPT-J

### 2021-10-05 paper.tex
expanded background a little

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\begin{document}

@@

\section{Execution Plan}
\subsection{Requirements \& Goals}
\subsubsection{Functional requirements (user stories)}
\begin{itemize}
\item As a finance researcher, I want to quantify the ability of news releases, SEC filings, and social media posts to move stock prices.
\item As an AI researcher, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can understand the power of GPT-J to understand complex real-world interactions.
\item As an algorithmic trader, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can make more-informed trading decisions.
\end{itemize}
\subsubsection{Non-functional requirements}
\begin{enumerate}
    \item[•] I will evaluate the correlations between the following items:
    \begin{enumerate}
        \item The release of SEC filings for company X and large movements in the stock price of company X.
        \item The release of news stories mentioning company X and large movements in the stock price of company X.
        \item The posting of tweets or other social media posts mentioning company X and large movements in the stock price of company X.
    \end{enumerate}
    \item[•] I evaluate the best ways of formatting prompts for GPT-J to increase output accuracy and consistency across varying inputs. Some options might include:
    \begin{enumerate}
        \item Providing a form for GPT-J to fill out appended to the end of the input data.
        \item Asking GPT-J a direct question appended to the end of the input data.
        \item Appending a universe current stock prices to the beginning of the input.
        \item Appending multiple news stories from the past days and weeks at the beginning of the input.
    \end{enumerate}
    \item[•] I will deploy the best model from my previous evaluations and test it on live stock market data. I will compare the model's performance against market indices like the S\&P 500. 
\end{enumerate}

\begin{figure}[H]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}
\section{Implementation}
\section{Conclusion}
The conclusion goes here.

>>>>

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\usepackage{flushend}
% \usepackage{balance}
\begin{document}

@@

By our estimation, the vast majortity of previous works involving sentiment analysis used a pre-processing step to extract sentiment from the news, and then embedded those features into a time-series dataset. News sources were often limited to headlines, tweets and small snippits because of the memory limitations of RNN sentiment classifiers. With the indruduction of large transformer networks \cite{Vaswani2017}, capable of processing large amounts of text like OpenAi's GPT-3 \cite{Brown2020} or GPT-J \cite{gpt-j}, we believe a new class of trading network can be created. Our method will encode the current world state in a large text-input wich combines sentiment, real-world facts, and stock price data into a single input. We believe that this new network can be trained to learn to trade like a human.

\section{Execution Plan}
\subsection{Requirements \& Goals}
\subsubsection{Functional requirements (user stories)}
\begin{itemize}
\item As finance researchers, we want to quantify the ability of news releases, SEC filings, and social media posts to move stock prices.
\item As AI researchers, we want to evaluate the viability of using GPT-J as a stock movement indicator so that we can understand the power of GPT-J to understand complex real-world interactions.
\item As algorithmic traders, we want to evaluate the viability of using GPT-J as a stock movement indicator so that I can make more-informed trading decisions.
\end{itemize}
\subsubsection{Non-functional requirements}
\begin{enumerate}
    \item[•] We will evaluate the correlations between the following items:
    \begin{enumerate}
        \item The release of SEC filings for company X and large movements in the stock price of company X.
        \item The release of news stories mentioning company X and large movements in the stock price of company X.
        \item The posting of tweets or other social media posts mentioning company X and large movements in the stock price of company X.
    \end{enumerate}
    \item[•] We will evaluate the best ways of formatting prompts for GPT-J to increase output accuracy and consistency across varying inputs. Some options might include:
    \begin{enumerate}
        \item Providing a form for GPT-J to fill out appended to the end of the input data.
        \item Asking GPT-J a direct question appended to the end of the input data.
        \item Appending a universe current stock prices to the beginning of the input.
        \item Appending multiple news stories from the past days and weeks at the beginning of the input.
    \end{enumerate}
    \item[•] We will deploy the best model from my previous evaluations and test it on live stock market data. I will compare the model's performance against market indices like the S\&P 500. 
\end{enumerate}

\begin{figure}[h]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}
\section{Implementation}
\section{Conclusion}
The conclusion goes here.
